Effects of Tunable Hydrophobicity on the Collective Hydrodynamics of Janus Particles under Flows

### 2022-08-05 doc/PRF2022/PRF_main.tex
combined intro sentence

\section{Introduction}
% Put \label in argument of \section for cross-referencing
%\section{\label{}}
Janus particles are colloids combining two dissimilar chemical or
physical functionalities at their opposite
sides~\cite{KirillovaMarschelkeSynytska2019}. Self-propelling Janus
particles, for example, with a permanent biphasic asymmetry, have
emerged as a rich chemical platform for the exploration of active
matter~\cite{Meredithetal2022}. In the absence of mobility and any
imposed flow, Janus particles often self-assemble into structures in a
viscous solvent with tunable functions for biomedical engineering
applications~\cite{GheisariSahfieeAbbasiEtAl2021_DMR,
LiuYangHuangEtAl2016_Angew, LiWangYaoEtAl2019_Nanoscale,
Bradley2016,Zarzaretal2015, KirillovaMarschelkeSynytska2019}. Depending
on the interactions between Janus particles (JPs) and the surrounding
viscous solvent, JPs self-assemble into oligomers of various geometries
and sizes~\cite{Bradley2017, KangHonciuc2018,
HongCacciutoLuijtenGranick2008}.

@@

We set $\max g>0$ to guarantee at least partial hydrophobicity of the JP
surface. Then, the boundary condition (BC) can be classified into three
categories: $\min g(\xx) = 0$, $\min g(\xx) >0$, and $\min g(\xx) <0$
where the extrema are taken for $\xx \in \Gamma_i$. These three
categories correspond to three characteristic values of $b$ in
\eqref{eq:bc-type}: $b=1$, $b=2$ and $b=0$, respectively. 
%
To see the effect of the shift parameter $b$, we simulate the dynamics
of 198 particles and 60 particles in a quiescent flow as shown in
Figure~\ref{fig:relax}. Three distinct configurations emerge: (i)
bilayer (amphiphilic) for $b = 1$, (ii) multilamellar (biased hydrophobic) for $b = 2$, and (iii) striated (bipolar)
for $b = 0$. Supplementary Movie S1 shows the self-assembly process for
the three cases. In the followings the terms ``multilamellar" and ``biased hydrophobic" are used  interchangeably to refer to BC (ii), while
``striated" and ``bipolar" are used interchangeably to refer to BC (iii).

>>>>

\section{Introduction}
% Put \label in argument of \section for cross-referencing
%\section{\label{}}
Janus particles are colloids combining two dissimilar chemical or
physical functionalities at their opposite
sides~\cite{KirillovaMarschelkeSynytska2019}. Self-propelling Janus
particles, for example, with a permanent biphasic asymmetry, have
emerged as a rich chemical platform for the exploration of active
matter~\cite{Meredithetal2022}.
In the absence of mobility and any
imposed flow, Janus particles (JPs) self-assemble
into oligomers of various geometries
and sizes
depending on the interactions between JPs and the 
viscous solvent~\cite{Bradley2017, KangHonciuc2018,
HongCacciutoLuijtenGranick2008},
with tunable functions for biomedical engineering
applications~\cite{GheisariSahfieeAbbasiEtAl2021_DMR,
LiuYangHuangEtAl2016_Angew, LiWangYaoEtAl2019_Nanoscale,
Bradley2016,Zarzaretal2015, KirillovaMarschelkeSynytska2019}.

@@

We set $\max g>0$ to guarantee at least partial hydrophobicity of the JP
surface. Then, the boundary condition (BC) can be classified into three
categories: $\min g(\xx) = 0$, $\min g(\xx) >0$, and $\min g(\xx) <0$
where the extrema are taken for $\xx \in \Gamma_i$. These three
categories correspond to three characteristic values of $b$ in
\eqref{eq:bc-type}: $b=1$, $b=2$ and $b=0$, respectively. 
%
To see the effect of the shift parameter $b$, we simulate the dynamics
of 198 particles and 60 particles in a quiescent flow as shown in
Figure~\ref{fig:relax}. Three distinct configurations emerge: (i)
bilayer (amphiphilic) for $b = 1$, (ii) multilamellar (biased hydrophobic) for $b = 2$, and (iii) striated (bipolar)
for $b = 0$. Supplementary Movie S1 shows the self-assembly process for
the three cases. In the following,
the terms ``multilamellar" and ``biased hydrophobic"
are used  interchangeably to refer to BC (ii), while
``striated" and ``bipolar" are used interchangeably to refer to BC (iii).
